Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-23 analysis/paper/paper.Rmd
Update to introduction section

The late Pleistocene of Southeast Asia is characterized by flaked stone tools which rarely have strongly patterned forms (Mijares 2008; Borel et al. 2013; Borel et al. 2017). This lack of clear typo-technological categories for flakes makes understanding the cultural dynamics of period difficult. Previous papers have employed multivariate analysis of flake outlines in relation to other variables, such as the traces of use wear and retouching (Borel et al. 2013; Borel et al. 2017). The purpose of our study is to examine the relationship between shape and lithic reduction in the assemblage at Mau A, northern Vietnam. We ask how flake shape correlates with reduction stage, artefact size and chronology.

>>>>

The late Pleistocene of Southeast Asia is characterized by flaked stone tools which rarely have strongly patterned forms (Mijares 2008; Borel et al. 2013; Borel et al. 2017). This lack of clear typo-technological categories for flakes makes understanding the cultural dynamics of period difficult. Previous papers have employed multivariate analysis of flake outlines in relation to other variables, such as the traces of use wear and retouching (Borel et al. 2013; Borel et al. 2017). Elliptical Fourier analysis was used to approximate shape outlines as sums of sine and cosine waves, with the coefficients from these sums being passed through Principal Component Analysis (Borel et al. 2013; Borel et al. 2017). This allowed the outlines of stone tools to be represented as points on a two-dimensional plane, facilitating comparisons between tool morphology and other variables, such as use wear. The use of outlines was intentional, as Borel et al. (2017) specifically highlighted the dangers of using raw linear measurements, such as length and width, to describe

The purpose of our study is to examine the relationship between shape and lithic reduction in the assemblage at Mau A, northern Vietnam. We ask how flake shape correlates with reduction stage, artefact size and chronology.
